### 2023-08-07 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
yny2

Next we consider a vesicle with a smaller reduced area $\alpha=0.4$ with the same geometry and $Ca=0.25$.
Figure~\ref{fig:RA4} shows  the shape of  
a (a) stiff single-component, (b) floppy single-component, and (c) multicomponent
vesicle at six locations along the stenosis channel. We first consider the three different energies---bending,
tension, and phase---for each of these cases. In
Figure~\ref{fig:Energy}, we plot these energies as a function of the
vesicle's center. As a reminder, the vesicle enters the constriction at
$x=-15$ and exits at $x=15$. Also note that the single-component
vesicles do not have a phase energy. 
%A few general trends can immediately be seen. 
First we observe that, as the vesicle enters the stenosis, it
develops regions of high curvature, and this results in an increase in
the bending energy. Secondly, since the stiff single-component and
multicomponent vesicles reach a steady-state shape near the middle of
the channel, their bending, tension, and phase energies remain nearly
constant from $x=0$ until the end of the stenosis.

%This corresponds to an arrest of phase coarsening for a vesicle confined in a stenosis.
The presence of the multiple lipid species in the multicomponent vesicle under confinement
results in interesting additional physics. The lipid species coarsens at
three instances, and this results in a decrease in the phase energy.
Note, however, that no coarsening occurs when the vesicle is in the
closely-fitting part of the domain. Each coarsening corresponds either
to two stiff regions overtaking a small floppy region, or to two floppy
regions overtaking a small stiff region. In the first case, a region
that was originally floppy has suddenly become stiff, and this results
in a sudden increase in the bending energy. In the latter case, because
of lipid conservation, the overtaken stiff region must relocate to the
another stiff-floppy interface, and this also results in a sudden
increase in the bending energy. These increases are visible in
Figure~\ref{fig:Energy}(c) as small upticks in the blue curve. However,
in both cases, the vesicle smooths out these new regions of high
curvature, but it takes some time since the diffusion time scale is
several orders of magnitude smaller than the bending relaxation time
scale.

>>>>

Next we consider a vesicle with a smaller reduced area $\alpha=0.4$ with the same geometry and $Ca=0.25$.
Figure~\ref{fig:RA4} shows  the shape of  
a (a) stiff single-component, (b) floppy single-component, and (c) multicomponent
vesicle at six locations along the stenosis channel. We first consider the three different energies---bending,
tension, and phase---for each of these cases. In
Figure~\ref{fig:Energy}, we plot these energies as a function of the
vesicle's center. As a reminder, the vesicle enters the constriction at
$x=-15$ and exits at $x=15$. Also note that the single-component
vesicles do not have a phase energy. 
%A few general trends can immediately be seen. 
First we observe that, as the vesicle enters the stenosis, it
develops regions of high curvature, and this results in an increase in
the bending energy. Secondly, as the stiff single-component and
multicomponent vesicles reach a steady-state shape near the middle of
the channel, their bending, tension, and phase energies remain nearly
constant from $x=0$ until the end of the stenosis. For the multiple-component vesicle,
this implies that there is no coarsening of lipid phase in the middle of a stenosis.

%This corresponds to an arrest of phase coarsening for a vesicle confined in a stenosis.
Such co-existence of multiple lipid domains in a vesicle under confinement
results in interesting additional physics. 
%
First we note that in Figure~\ref{fig:Energy}(c),
the lipid species coarsens at
three instances, and this results in a decrease in the phase energy.
However, as we mentioned earlier, no coarsening occurs when the vesicle is in the
closely-fitting part of the channel. Each coarsening corresponds either
to two stiff regions overtaking a small floppy region, or to two floppy
regions overtaking a small stiff region. In the first case, a region
that was originally floppy has suddenly become stiff, and this results
in a sudden increase in the bending energy. In the latter case, because
of lipid conservation, the overtaken stiff region must relocate to the
another stiff-floppy interface, and this also results in a sudden
increase in the bending energy. These increases are visible in
Figure~\ref{fig:Energy}(c) as small upticks in the blue curve. However,
in both cases, the vesicle smooths out these new regions of high
curvature, but it takes some time since the diffusion time scale is
several orders of magnitude smaller than the bending relaxation time
scale.
